---
title: "PLOS Pathogens Review"
output: html_document
---

```{r setup, message = FALSE, warning = FALSE, echo = FALSE}

library(VaccComp)
library(ggboot)
library(plyr)
library(tidyr)
library(stringr)
library(magrittr)
library(dplyr)
library(VaccCompData)
library(cowplot)
library(doParallel)

knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>", 
  cache = TRUE, 
  echo = TRUE,
  message = FALSE, 
  warning = FALSE, 
  tidy = FALSE
)
```

```{r save, echo = FALSE}
save = TRUE
getSavePath = function(x) str_c( "C:/Users/migue/Dropbox/Rodo et al Vaccine Immune Response paper/Figures/Final/R/", x, ".pdf" )
```

# Minor comments

## 2.2 - Age effect

### Size

```{r 2.2-size-dataprep-both, eval = FALSE}
ageTbl <- tmax17ExcTbl %>% 
  filter( vaccine %in% c( 2, 3, 5 ) ) %>%
  group_by( vaccine, prid, infxn, ptid ) %>%
  summarise( resp = sum( resp ) ) %>%
  ungroup() 

ageTbl %>%
  group_by( vaccine, prid, age ) %>%
  slice(1) %>%
  ungroup()

ageTbl %<>%
  mutate( age = -1 ) %>%
  mutate( age = Vectorize(ifelse)( vaccine == 2, 
                                   "1", age ), 
          age = Vectorize(ifelse)( vaccine == 5, 
                                   "0", age ), 
          age = Vectorize(ifelse)( prid == 3, 
                                   "1", age ), 
          age = Vectorize(ifelse)( prid == 4, 
                                   "0", age ) ) # add age group

ageTbl %<>%
  mutate( comp = -1 ) %>%
  mutate( comp = Vectorize(ifelse)( vaccine == 3, "3", comp ), 
          comp = Vectorize(ifelse)( vaccine == 2, "h", comp ), 
          comp = Vectorize(ifelse)( vaccine == 5, "h", comp ), )

age22LabVec <- c( "1" = "Adults", "0" = "Adolescents")
age22ColVec <- c( "1" = "orange", "0" = "dodgerblue" )
comp22ColVec <- c( "3" = "orange", "h" = "dodgerblue" )
comp22LabVec <- c( "3" = "M72/AS01E", "h" = "H(56/1):IC31")
```

```{r 2.2-size-uv-both, eval = FALSE}
# plot
set.seed(2)
scaleFactor = 0.56^-1
legendTextSize = 8 * scaleFactor
stripTextSize = 8 * scaleFactor
axisTitleTextSize = 8 * scaleFactor
fontScaleFactor = 0.65 * scaleFactor 
startTime <- proc.time()[3]
ggbootUV( data = ageTbl, 
  resp = resp, xAxis = comp, col = comp, facet = infxn, diff = age, pMethod = "percT", ciMethod = "bca",
  B = 5e3, altSide = 'high', eqErrBarWidth = TRUE, errBarLineType = "11", remXAxisMarks = TRUE, seB = 5e2, calcStat = "mean", trim = 0.2,
  rotXText = TRUE, pointSize = 3, errBarSize = 1.5, yLab = "Increase in vaccine-induced memory\nCD4 T cell response (%) for adults over adolescents", 
  nullValue = 0, xLab = "Vaccine", xAxisLabVec = comp22LabVec, errBarAlpha = 0.88,
  colLabName = "", colourVec = comp22ColVec, colLabVec = comp22LabVec, 
  facetLabVec = infLabelVec, nCol = 3, facetScale = 'free_x', fontScaleFactor = fontScaleFactor, 
  lineScaleFactor = 2, plotTblName = "fig3aTbl" ) +
  theme( legend.key.height = unit( 6, "mm" ), 
    legend.key.width = unit( 9, "mm" ), 
    legend.text = element_text( size = legendTextSize ),
    strip.text = element_text( size = stripTextSize, colour = 'black' ), 
    legend.title = element_blank(), 
    legend.text.align = 0, 
    axis.title = element_text( size = axisTitleTextSize), 
    strip.background = element_rect(linetype = 'solid', size = 1, fill = 'white', 
       colour = 'white' ) ) + 
    guides( linetype = guide_legend(override.aes = list(size=1.8)), 
      colour = guide_legend( order = 1 ) )  
proc.time()[3] - startTime
cowplot::ggsave( "C:/Users/migue/Dropbox/Rodo et al Vaccine Immune Response paper/Figures/Revisions/R/size-uv-age-diff-2.pdf", units = "cm", width = 16, height= 13, scale = 1 )

```

## 3.4

### Stats

#### Pre-vaccination

Prepare the data to calculate the statistics for the pre-vaccination responses. 
```{r 3.4-pv-data}
# infected

## long table
lTbl1 = bl17ExcITbl %>%
  filter( cd == 4 & infxn == 1 ) %>%
  mutate( cytCombo = str_sub( cytCombo, 4 ), 
          vaccStim = str_c( vaccine, stim ) ) %>%
  group_by(  vaccine, infxn, ptid, stim, vaccStim ) %>%
  summarise( resp = sum( resp ) ) %>% 
  ungroup() 

# uninfected

## long table
lTbl0 = bl17ExcITbl %>%
  filter( cd == 4 & infxn == 0 ) %>%
  mutate( cytCombo = str_sub( cytCombo, 4 ), 
          vaccStim = str_c( vaccine, stim ) ) %>%
  group_by(  vaccine, infxn, ptid, stim, vaccStim ) %>%
  summarise( resp = sum( resp ) ) %>% 
  ungroup() 

```

Use `ggboot::ggbootUV` to calculate the point estimates, confidence intervals and statistical significance, and save as table `fig34PVTbl`.
```{r 3.4-pv-stats}
# plot
set.seed(2)
scaleFactor = 0.56^-1
legendTextSize = 8 * scaleFactor
stripTextSize = 8 * scaleFactor
axisTitleTextSize = 8 * scaleFactor
fontScaleFactor = 0.56 * scaleFactor
xAxisTextSize = 8 * scaleFactor
p0 = ggbootUV( data = full_join( lTbl0, lTbl1 ), 
  resp = resp, xAxis = vaccStim, col = vaccine, facet = infxn, pMethod = "percT", ciMethod = "bca",
  B = 5e3, altSide = 'high', eqErrBarWidth = TRUE, errBarLineType = "11", remXAxisMarks = FALSE, seB = 5e2, calcStat = "mean", trim = 0.2,
  rotXText = TRUE, pointSize = 3, errBarSize = 1.5, yLab = "Pre-vaccination\nCD4 T cell response (%)", 
  nullValue = 0.005, xLab = "Vaccine", xAxisLabVec = vaccStim2StimLabVec, errBarAlpha = 0.88,
  colLabName = "", colourVec = vaccColVec, colLabVec = fullVaccLabelVec, 
  facetLabVec = infLabelVec, nCol = 3, facetScale = 'free_x', fontScaleFactor = fontScaleFactor, 
  lineScaleFactor = 2, plotTblName = "fig34PVTbl" ) +
  theme( legend.key.height = unit( 6, "mm" ), 
    legend.key.width = unit( 9, "mm" ), 
    legend.text = element_text( size = legendTextSize ),
    strip.text = element_text( size = stripTextSize, colour = 'black' ), 
    legend.title = element_blank(), 
        legend.text.align = 0, 
    axis.title = element_text( size = axisTitleTextSize), 
    strip.background = element_rect(linetype = 'solid', size = 1, fill = 'white', 
       colour = 'white' ), 
    axis.text.x = element_text( hjust = 1, angle = 90, vjust = 0.45 ) ) + 
    guides( linetype = guide_legend(override.aes = list(size=1.8)), 
      colour = guide_legend( order = 1 ) )  
```

#### Vaccine-induced memory

Prepare the data to calculate the statistics for the vaccine-induced memory responses. 
```{r 3.4-vim-data}
# infected

## long table
lTbl1 = tmaxSub17ExcITbl %>%
  filter( cd == 4 & infxn == 1 ) %>%
  mutate( cytCombo = str_sub( cytCombo, 4 ), 
          vaccStim = str_c( vaccine, stim ) ) %>%
  group_by(  vaccine, infxn, ptid, stim, vaccStim ) %>%
  summarise( resp = sum( resp ) ) %>% 
  ungroup() 

# uninfected

## long table
lTbl0 = tmaxSub17ExcITbl %>%
  filter( cd == 4 & infxn == 0 ) %>%
  mutate( cytCombo = str_sub( cytCombo, 4 ), 
          vaccStim = str_c( vaccine, stim ) ) %>%
  group_by(  vaccine, infxn, ptid, stim, vaccStim ) %>%
  summarise( resp = sum( resp ) ) %>% 
  ungroup() 

```

Use `ggboot::ggbootUV` to calculate the point estimates, confidence intervals and statistical significance, and save as table `fig34VIMTbl`.
```{r 3.4-vim-stats}
# plot
set.seed(2)
scaleFactor = 0.56^-1
legendTextSize = 8 * scaleFactor
stripTextSize = 8 * scaleFactor
axisTitleTextSize = 8 * scaleFactor
fontScaleFactor = 0.56 * scaleFactor
xAxisTextSize = 8 * scaleFactor
p0 = ggbootUV( data = full_join( lTbl0, lTbl1 ) %>% filter( vaccine != 8 ), 
  resp = resp, xAxis = vaccStim, col = vaccine, facet = infxn, pMethod = "percT", ciMethod = "bca",
  B = 5e3, altSide = 'high', eqErrBarWidth = TRUE, errBarLineType = "11", remXAxisMarks = FALSE, seB = 5e2, calcStat = "mean", trim = 0.2,
  rotXText = TRUE, pointSize = 3, errBarSize = 1.5, yLab = "Vaccine-induced memory\nCD4 T cell response (%)", 
  nullValue = 0, xLab = "Vaccine", xAxisLabVec = vaccStim2StimLabVec, errBarAlpha = 0.88,
  colLabName = "", colourVec = vaccColVec, colLabVec = fullVaccLabelVec, 
  facetLabVec = infLabelVec, nCol = 3, facetScale = 'free_x', fontScaleFactor = fontScaleFactor, 
  lineScaleFactor = 2, plotTblName = "fig34VIMTbl" ) +
  theme( legend.key.height = unit( 6, "mm" ), 
    legend.key.width = unit( 9, "mm" ), 
    legend.text = element_text( size = legendTextSize ),
    strip.text = element_text( size = stripTextSize, colour = 'black' ), 
    legend.title = element_blank(), 
    axis.title = element_text( size = axisTitleTextSize), 
    strip.background = element_rect(linetype = 'solid', size = 1, fill = 'white', 
       colour = 'white' ), 
    legend.text.align = 0, 
    axis.text.x = element_text( hjust = 1, angle = 90, vjust = 0.45 ) ) + 
    guides( linetype = guide_legend(override.aes = list(size=1.8)), 
      colour = guide_legend( order = 1 ) )  
```

### Plots

#### Data 

Prepare `fig34PVTbl` and `fig34VIMTbl` for plotting. Result saved as `fig34Tbl`. 
```{r 3.4-data}
fig34Tbl <- bind_rows( fig34PVTbl %>% 
                         mutate( timePoint = 0 ), 
                       fig34VIMTbl %>%
                         mutate( timePoint = 1 ) ) %>% # set timePoint variable to distinguish pre-vaccination from vaccine-induced memory response
  mutate( vaccine = str_sub( split, start = -3, end = -3 ), 
          infxn = str_sub( split, start = -1, end = -1 ) ) # get vaccine and infxn status from split variable
```

#### Ag85

Plot the point estimates, confidence intervals and statistical significance of the pre-vaccination and vaccine-induced memory responses for the vaccines containing Ag85A/B, using `fig34PVTbl` and `fig34VIMTbl` obtained above. 
```{r 3.4-ag85-plot}
scaleFactor <- 0.56^-1
p0 <- ggplot( fig34Tbl %>%
                 filter( timePoint == "0" &
                           str_detect( split, "ag85" ) ), aes( x = vaccine, col = vaccine ) ) +
  geom_hline( yintercept = 0, linetype = 'dashed', 0.6 ) +
  geom_point( aes( y = origStat ), size = 2 ) +
  geom_errorbar( aes( ymin = lb, ymax = ub, linetype = sig  ), size = 1, alpha = 0.88 ) +
  facet_wrap( ~infxn, ncol = 2, labeller = labeller( infxn = infLabelVec ) ) +
  theme( axis.text.x = element_blank(), 
         axis.ticks.x = element_blank(), 
         legend.key.width = unit( 6, "mm" ), 
    strip.text = element_text( size = 8 * scaleFactor, colour = 'black' ), 
    legend.title = element_blank(), 
    axis.title = element_text( size = 8 * scaleFactor ), 
    strip.background = element_rect( linetype = 'solid', size = 1, fill = 'white', 
       colour = 'white' ), 
    legend.text = element_text( size = 8 * scaleFactor) ) +
  labs( x = "Vaccine", y = "Pre-vaccination\nCD4 T cell response (%)" ) +
  scale_colour_manual( labels = fullVaccLabelVec, 
                       values = vaccColVec ) +
  scale_linetype_manual( labels = c( "0" = "Not significant", "1" = "Significant" ),
        values = c( "0" = "dotted", '1' = 'solid' ),
        drop = FALSE,
        limits = c( "0", "1" ) )

p1 <- ggplot( fig34Tbl %>%
                 filter( timePoint == "1" &
                           str_detect( split, "ag85" ) ), aes( x = vaccine, col = vaccine ) ) +
  geom_hline( yintercept = 0, linetype = 'dashed', 0.6 ) +
  geom_point( aes( y = origStat ), size = 2 ) +
  geom_errorbar( aes( ymin = lb, ymax = ub, linetype = sig  ), size = 1, alpha = 0.88 ) +
  facet_wrap( ~infxn, ncol = 2, labeller = labeller( infxn = infLabelVec ) ) +
  theme( axis.text.x = element_blank(), 
         axis.ticks.x = element_blank(), 
         legend.key.width = unit( 6, "mm" ), 
    strip.text = element_text( size = 8 * scaleFactor, colour = 'black' ), 
    legend.title = element_blank(), 
    axis.title = element_text( size = 8 * scaleFactor ), 
    strip.background = element_rect( linetype = 'solid', size = 1, fill = 'white', 
       colour = 'white' ), 
    legend.text = element_text( size = 8 * scaleFactor) ) +
  labs( x = "Vaccine", y = "Vaccine-induced memory\nCD4 T cell response (%)" ) +
  scale_colour_manual( labels = fullVaccLabelVec, 
                       values = vaccColVec ) +
  scale_linetype_manual( labels = c( "0" = "Not significant", "1" = "Significant" ),
        values = c( "0" = "dotted", '1' = 'solid' ),
        drop = FALSE,
        limits = c( "0", "1" ) )

p2 <- plot_grid( p0, p1, ncol = 1, labels = c( "A", "B" ) )
```

Save the above plot as S10_Fig.pdf into Dropbox/Rodo et al Vaccine Immune Response Paper/Figures/Final/R.
```{r  3.4-ag85-save, eval = save, echo = FALSE, dependson = c( "setup", "save" )}
cowplot::ggsave( getSavePath( "S10_Fig" ), units = "cm", width = 13, height= 10, scale = 1.85, dpi = 300 )
```

#### ESAT-6

Plot the point estimates, confidence intervals and statistical significance of the pre-vaccination and vaccine-induced memory responses for the vaccines containing Ag85A/B, using `fig34PVTbl` and `fig34VIMTbl` obtained above. 
```{r 3.4-esat6-plot}
scaleFactor <- 0.56^-1
p0 <- ggplot( fig34Tbl %>%
                 filter( timePoint == "0" &
                           str_detect( split, "esat6" ) ), aes( x = vaccine, col = vaccine ) ) +
  geom_hline( yintercept = 0, linetype = 'dashed', 0.6 ) +
  geom_point( aes( y = origStat ), size = 2 ) +
  geom_errorbar( aes( ymin = lb, ymax = ub, linetype = sig  ), size = 1, alpha = 0.88 ) +
  facet_wrap( ~infxn, ncol = 2, labeller = labeller( infxn = infLabelVec ) ) +
  theme( axis.text.x = element_blank(), 
         axis.ticks.x = element_blank(), 
         legend.key.width = unit( 6, "mm" ), 
    strip.text = element_text( size = 8 * scaleFactor, colour = 'black' ), 
    legend.title = element_blank(), 
    axis.title = element_text( size = 8 * scaleFactor ), 
    strip.background = element_rect( linetype = 'solid', size = 1, fill = 'white', 
       colour = 'white' ), 
    legend.text = element_text( size = 8 * scaleFactor) ) +
  labs( x = "Vaccine", y = "Pre-vaccination\nCD4 T cell response (%)" ) +
  scale_colour_manual( labels = fullVaccLabelVec, 
                       values = vaccColVec ) +
  scale_linetype_manual( labels = c( "0" = "Not significant", "1" = "Significant" ),
        values = c( "0" = "dotted", '1' = 'solid' ),
        drop = FALSE,
        limits = c( "0", "1" ) )

p1 <- ggplot( fig34Tbl %>%
                 filter( timePoint == "1" &
                           str_detect( split, "esat6" ) ), aes( x = vaccine, col = vaccine ) ) +
  geom_hline( yintercept = 0, linetype = 'dashed', 0.6 ) +
  geom_point( aes( y = origStat ), size = 2 ) +
  geom_errorbar( aes( ymin = lb, ymax = ub, linetype = sig  ), size = 1, alpha = 0.88 ) +
  facet_wrap( ~infxn, ncol = 2, labeller = labeller( infxn = infLabelVec ) ) +
  theme( axis.text.x = element_blank(), 
         axis.ticks.x = element_blank(), 
         legend.key.width = unit( 6, "mm" ), 
    strip.text = element_text( size = 8 * scaleFactor, colour = 'black' ), 
    legend.title = element_blank(), 
    axis.title = element_text( size = 8 * scaleFactor ), 
    strip.background = element_rect( linetype = 'solid', size = 1, fill = 'white', 
       colour = 'white' ), 
    legend.text = element_text( size = 8 * scaleFactor) ) +
  labs( x = "Vaccine", y = "Vaccine-induced memory\nCD4 T cell response (%)" ) +
  scale_colour_manual( labels = fullVaccLabelVec, 
                       values = vaccColVec ) +
  scale_linetype_manual( labels = c( "0" = "Not significant", "1" = "Significant" ),
        values = c( "0" = "dotted", '1' = 'solid' ),
        drop = FALSE,
        limits = c( "0", "1" ) )

p2 <- plot_grid( p0, p1, ncol = 1, labels = c( "A", "B" ) )
```

Save the above plot as S11_Fig.pdf into Dropbox/Rodo et al Vaccine Immune Response Paper/Figures/Final/R.
```{r  3.4-esat6-save, eval = save, echo = FALSE, dependson = c( "setup", "save" )}
cowplot::ggsave( getSavePath( "S11_Fig" ), units = "cm", width = 13, height= 10, scale = 1.85, dpi = 300 )
```





