---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-", 
  tidy = TRUE
)
```

# VaccComp

VaccComp provides the code used to create the figures for the paper 'A comparison of antigen-specific T cell responses of six novel tuberculosis vaccine candidates'. It can be installed from Github using the following code:

```{r echo = TRUE, eval = FALSE}
devtools::install_github( "MiguelRodo/VaccComp" )
```

Two packages, ggboot and VaccCompData, are not available on CRAN but are required to re-compile the figures. They can be installed by running the following code:

```{r echo = TRUE, eval = FALSE}
devtools::install_github( "MiguelRodo/VaccCompData", build_vignettes = TRUE )
devtools::install_github( "MiguelRodo/ggboot" )
```

The analysis code is available as the file at the path VaccComp/Analysis/Paper_Figures.Rmd. 

